### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Doc

\subsection{Sprint 3: Sampling and Literature Collection}

\subsection{Sprint 4: Write Article}

>>>>

\subsection{Sprint 3: Sampling and Literature Collection}
This sprint encompasses the collection of all relevant literature required to effectively answer the question posed in the article and the research project. 
\\\\
The initial collection of literature was only comprised of the three fields mentioned above. Once this step was completed, a literature review on the collected studies and articles was written. During this, only certain theories or models were discussed from the relevant fields based on whether they would be helpful when answering the question of this research. As such, a robust instructional theory and a theory dealing with motivation were discussed from pedagogy. Explanations of the field of ludology in addition to the topics of serious games and games as simulations. From gamification, the different classifications of knowledge and how they can each be effectively taught using games was taken. 
\\\\
Academic papers in which a serous game was designed and/or implemented were also examined during this phase. This was done to gain insight into what design philosophies serious games typically make use of and how that affects the successfulness of the game. 
\\\\
It was also during this sprint that an informal look at video game tutorials took place for additional hands-on understanding. This was done as the digital games distributor, Steam, held an event titled "Next Fest" which features demonstrations of many soon to release games and as such were mainly tutorial sections which aimed to teach players the controls of the games. While this information was not explicitly used in the study, it did provide certain practical understanding of how select types of games may be structured.
\\\\
This sprint was concluded when the literature study was to be submitted.

\subsection{Sprint 4: Write Article}
This sprint, being the Development step of the design science process, saw an article based off of the research already done until this point be written. 
\\\\
This phase included the writing of the article from the introduction until the findings section. As such, the content covered at this point was the problem statement, a suggestion to address it, the literature needed to address it and the aforementioned case studies. The methodology for the synthesis process was also described during this phase and as such it included the following steps:
\begin{enumerate}
\item Literature surrounding the applicable fields was researched (Already completed at this point)
\item Case studies concerning serious games was studied and similarities noted (Already completed at this point)
\item Select theories that aid this process were pinpointed 
\item From this research, recommendations for the knowledge domains were made
\end{enumerate}

\noindent The remaining two phases are a part of the following sprint in development as this sprint was concluded when the above was completed.
